Space is the Place: Effects of Continuous Spatial Structure on Analysis of Population Genetic Data

### 2020-02-19 ms/spaceness.tex
tv edits

Also note that $\sigma$ controls the dispersal of offspring away from only \emph{one} parent \llabel{ll:sigma_effective}
(e.g., the seed parent for plants),
while the usual population genetics definition of dispersal distance
involves the distance to a randomly chosen one of the two parents.
(thus taking into account the distance from pollen parent as well).
This second component -- the distance between mates --
has in our simulations a distribution that is of order $\sigma$ but that depends on the population's patchiness.
If both between-mate distance and dispersal distance has variance $\sigma^2$ along each axis,
then the mean squared distance to a randomly chosen parent along that axis would be
$(\sigma^2 + 2 \sigma^2)/2 = 3 \sigma^2 /2$.
Also note that Wright's definition of neighborhood size should rightly use the \emph{effective}
dispersal distance, i.e., the mean squared displacement along an axis
between parent-child pairs found moving back along a lineage \citep{barton2002neutral}.
Nonetheless, we use $\sigma$ and $\rho$ as defined here to compute $N_W$
because these quantities are more easily observable in practice than their ``effective'' versions.
We also note that effective population density is lower than the actual population density,
while the $\sigma$ we use is an underestimate,
so our numbers may be close to the ``effective'' values used in theory.

>>>>

 Note that $\sigma$ controls the dispersal of offspring away from only \emph{one} parent \llabel{ll:sigma_effective}
(e.g., the seed parent for plants),
while population genetics usually defines "dispersal distance" to be the distance to a randomly chosen one of the two parents
(thus taking into account the distance from pollen parent as well).
This second component -- the distance between mates --
has in our simulations a distribution that is of order $\sigma$ but that depends on the population's patchiness.
If both between-mate distance and dispersal distance has variance $\sigma^2$ along each axis,
then the mean squared distance to a randomly chosen parent along that axis would be
$(\sigma^2 + 2 \sigma^2)/2 = 3 \sigma^2 /2$.
To match theory, neighborhood size should be defined in terms of \emph{effective}
dispersal distance, i.e., the mean squared displacement along an axis
between parent-child pairs found moving back along a lineage \citep{barton2002neutral}, 
and \emph{effective} population density \citep{Rousset1997}.
However, we use $\sigma$ and $\rho$ as defined here to compute $N_W$
because these quantities are more easily observable in practice than their ``effective'' versions.
